### 2022-06-20 README.Rmd
New version 0.4.0

`onsetsync` is a R package for musical dynamics involving synchrony. There are functions for common operations such as adding isochronous beats based on metrical structure, adding annotations, calculating classic measures of synchrony between two performers, and assessing periodicity of the onsets, and visualising synchrony across cycles, time, or another property.

@@

Note that `onsetsync` is not dedicated to extraction of onsets from audio as that can be done in other packages (e.g. [Librosa](https://librosa.org), or [Mir Toolbox for Matlab](https://www.jyu.fi/hytk/fi/laitokset/mutku/en/research/materials/mirtoolbox), or [Sonic Visualiser](https://www.sonicvisualiser.org) using well-known onset detection algorithms. Here we take it as granted that we have extracted the onsets in some of these programs, probably checked them by hand, and we have the onset times recorded into csv files.

```{r, message=FALSE, warning=FALSE,echo=TRUE}
library(onsetsync)
library(httr)
library(dplyr)
library(ggplot2)
```

@@

There are several variants of this summary that create different summaries of the onsets across the beats, but let's move on.

To what degree are the pairs of instruments synchronised in this example? Since the instruments usually play widely different amounts of onsets in a piece, and these are bound to be at different beats sub-divisions, the mutual amount of comparable onsets for each pair varies often dramatically. In order to keep the mean and standard deviations comparable, we will randomly sample joint onsets for both instruments.

>>>>

`onsetsync` is a R package for musical dynamics involving synchrony. <img src="man/figures/logo.png" align="right" height="139"/> There are functions for common operations such as adding isochronous beats based on metrical structure, adding annotations, calculating classic measures of synchrony between two performers, and assessing periodicity of the onsets, and visualising synchrony across cycles, time, or another property.

@@

Note that `onsetsync` is not dedicated to extraction of onsets from audio as that should be done using other tools (e.g. [Librosa](https://librosa.org), or [MIR Toolbox for Matlab](https://www.jyu.fi/hytk/fi/laitokset/mutku/en/research/materials/mirtoolbox), or [Sonic Visualiser](https://www.sonicvisualiser.org) using established onset detection algorithms). Here we take it as granted that we have extracted the onsets of the music from a recording in some of these tools, probably checked them by hand, and we have the onset times recorded into csv files.

```{r, message=FALSE, warning=FALSE,echo=TRUE}
library(onsetsync)
library(httr)
library(dplyr)
library(ggplot2)
packageVersion("onsetsync")
```
Read onsets of one Cuban Son performance titled _Palo Santo_ from _IEMP_ dataset about _Cuban Son and Salsa_ at [https://osf.io/sfxa2/](https://osf.io/sfxa2/):

Add annotations of the metric cycles to the data, also obtained from OSF dataset:

@@

There are several variants of this visualisation that create alternative summaries of the onsets across the beats, but let's move on.

To what degree are the pairs of instruments synchronised to each other in this example? Since the instruments usually play widely different amounts of onsets in a piece, and these are bound to be at different beats sub-divisions, the mutual amount of comparable onsets for each pair varies often dramatically. In order to keep the mean and standard deviations comparable, we will randomly sample joint onsets for both instruments.
